Gravitational disturbance

### 2018-03-23 manuscript/manuscript.tex
remove the term gravitational disturbance

%\documentclass[manuscript]{geophysics}
%\usepackage[nomarkers]{endfloat}

% For a two-column format that looks like the final product, uncomment bellow
% and comment the two lines above
\documentclass[paper,twocolumn,twoside]{geophysics}

@@

The resultant of gravitational force and centrifugal force acting 
on a body at rest on the Earth's surface is called gravity vector
and its intensity is called simply gravity 
\citep{hofmann-wellenhof-moritz2005}.
In the case of gravimetry on moving platforms (e.g., airplanes,
helicopters, marine vessels), there are additional
non-gravitational accelerations due to the vehicle motion, 
such as Coriolis acceleration and high-frequency vibrations 
\citep{glennie-etal2000, nabighian-etal2005-grav, baumann_etal2012}.
Gravity is the most commonly measured quantity in
geophysical surveying.
Geophysicists use gravity for estimating the Earth's 
internal density distribution whereas geodesists use
gravity to estimate the geoid \citep{li2001}
Hence, geophysicists are usually interested 
in the gravitational component of the observed gravity 
which is produced by the Earth's internal 
density distribution.
The first step of the procedure for isolating the
gravitational component of the observed gravity 
consists in removing the non-gravitational effects due 
to the vehicle motion and also the time variations
such as Earth tides, instrumental drift and barometric 
pressure changes, for example.
If these effects are properly removed, the resultant 
gravity data can be considered as the sum of a 
centrifugal component due to the Earth's rotation and
a gravitational component produced by the whole Earth's
internal density distribution.
%For simplicity, we will henceforth call this 
%resultant gravity corrected from non-gravitational 
%effects due to the vehicle motion and also time variations
%as simply gravity.

In applied geophysics, gravity surveys are usually conducted 
over small areas on the Earth's surface for the purpose of 
characterizing geological structures located within the
crust and upper mantle.
Consequently, geophysicists are only interested in the
particular gravitational component of gravity which 
is produced by these target geological structures.
The isolation of this particular gravitational component 
and its subsequent use for estimating density 
distributions related to geological structures in subsurface 
are the main goals in applied geophysics 
\citep{blakely1996}.

In this paper, we discuss the theoretical definition
of the gravitational disturbance based on the 
well-established concepts of normal Earth, normal gravity, 
gravity disturbance and gravity anomalies.
The concept of gravitational disturbance plays an
important role in the discussions about 
the use of gravity disturbance or gravity anomalies
in geophysical applications.
It seems that this theoretical issue has been 
debated within the scientific community from a 
more geodetic than geophysical point of view
\citep{lafehr1991, chapin1996, li2001, fairhead2003,
hackney-featherstone2003, hinze2005}.
Our reasoning suggests that the gravity 
disturbance is conceptually more appropriated than 
gravity anomalies for approximating
the gravitational disturbance and use it for estimating 
density distributions in subsurface.

>>>>

\documentclass[manuscript]{geophysics}
\usepackage[nomarkers]{endfloat}

% For a two-column format that looks like the final product, uncomment bellow
% and comment the two lines above
%\documentclass[paper,twocolumn,twoside]{geophysics}

@@

The resultant of gravitational force and centrifugal force acting 
on a body at rest on the Earth's surface is called gravity vector
and its intensity is called simply gravity 
\citep{hofmann-wellenhof-moritz2005}.

In the case of gravimetry on moving platforms (e.g., airplanes,
helicopters, marine vessels), there are additional
non-gravitational accelerations due to the vehicle motion, 
such as Coriolis acceleration and high-frequency vibrations 
\citep{glennie-etal2000, nabighian-etal2005-grav, baumann_etal2012}.

Gravity is the most commonly measured quantity in geophysical surveying.
Geophysicists use gravity for estimating the Earth's 
internal density distribution whereas geodesists use
gravity to estimate the geoid \citep{li2001}.

Hence, geophysicists are usually interested 
in the gravitational component of the observed gravity 
which is produced by the Earth's internal 
density distribution.

The first step of the procedure for isolating this 
gravitational component consists in removing the non-gravitational effects due 
to the vehicle motion and also the time variations
such as Earth tides, instrumental drift and barometric 
pressure changes, for example.

If these effects are properly removed, the resultant 
gravity data can be considered as the sum of a 
centrifugal component due to the Earth's rotation and
a gravitational component produced by the whole Earth's
internal density distribution.

%For simplicity, we will henceforth call this 
%resultant gravity corrected from non-gravitational 
%effects due to the vehicle motion and also time variations
%as simply gravity.

In applied geophysics, gravity surveys are usually conducted 
over small areas on the Earth's surface for the purpose of 
characterizing geological structures located within the
crust and upper mantle.

Consequently, geophysicists are only interested in the
particular gravitational component of gravity which 
is produced by these target geological structures.

The isolation of this particular gravitational component 
and its subsequent use for estimating density 
distributions related to geological structures in subsurface 
are the main goals in applied geophysics 
\citep{blakely1996}.

In this paper, we present a discussion based on the
well-established concepts of normal Earth, normal gravity, gravity disturbance and gravity anomalies aiming at bringing some
light to the following question: in geophysical applications,
should we use gravity disturbance or gravity anomaly?

It seems that this theoretical issue has been 
debated within the scientific community from a 
more geodetic than geophysical point of view
\citep{lafehr1991, chapin1996, li2001, fairhead2003,
hackney-featherstone2003, hinze2005}.

Our reasoning suggests that the gravity 
disturbance is conceptually more appropriated than 
gravity anomalies for approximating
the gravitational disturbance and use it for estimating 
density distributions in subsurface.
